\bf\mftitle

### 2011-03-01 doc/jInfer/treeruledisplayer/treeruledisplayer.tex
Tree RD documentation: fixing a minor problem.
3187368 - Review documentation: cleanup - treeruledisplayer done

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Michal Švirec \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer \\ \hline
Module dependencies:   & Base \\
	& JUNG \\ \hline
Public packages:       & none \\ \hline
\end{tabular}

@@

All the trees representing rules are created in the \code{GraphBuilder} class using the \code{buildGraphPanel()} method. This method creates \code{DelegateForrest} of \code{DelegateTree}s where each tree of the forrest represents one rule. Each vertex of the tree is represented by \code{Regexp<?\ extends AbstractNamedNode>} and edge by \code{RegexpInterval}. While the code building tree structure is a nice recursion programming exercise, there is nothing of a special interest in it. Finally the method appends forrest into layout and VisualizationViewer which were described above. All code responsible for building rule trees is contained in the \code{cz.cuni.mff.ksi.jinfer.treeruledisplayer.logic}. For more details about JUNG library please see \cite{jung}.\\

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Michal Švirec \\ \hline
Required tokens       & none \\ \hline
Provided tokens       & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer} \\ \hline
Module dependencies   & Base \\
	& JUNG \\ \hline
Public packages       & none \\ \hline
\end{tabular}

@@

All the trees representing rules are created in the \code{GraphBuilder} class using the \code{buildGraphPanel()} method. This method creates \code{DelegateForrest} of \code{DelegateTree}s where each tree of the forrest represents one rule. Each vertex of the tree is represented by \code{Regexp<?\ extends AbstractNamedNode>} and edge by \code{RegexpInterval}. While the code building tree structure is a nice recursion programming exercise, there is nothing of a special interest in it. Finally the method appends forrest into layout and \code{VisualizationViewer} which were described above. All code responsible for building rule trees is contained in the \code{cz.cuni.mff.ksi.jinfer.treeruledisplayer.logic}. For more details about JUNG library please see \cite{jung}.\\
